---
title: "Data1 analysis"
output: html_document
---
#Data analysis and figure creation for Color Memory and Emotion Experiment on Youtube

###Kayli Peters

##Introduction
This file was used to analyze data from my Color Memory and Emotion Experiment, 
https://www.youtube.com/watch?v=U6WmtoIuaXY.  
All materials, including consent, tasks, and debriefing can be accessed 
in the previous link provided.  **Note**: The link may not be accessible on mobile devices.  It is suggested to 
work on a laptop or desktop computer.  

These data represent 35 participants who reported participating 
in existing conditions and emailed me their data.  
Those participants that did not include the condition
were not included in this data set.  

Although several variables were included.  Only two were of interest to
be analyzed here.  The variables representing Congruence and Recall(Remember) were the 2 analyzed.  These data were analyzed and presented on the poster.  

###Preparing data for analysis 

```{r}
d<-read.csv("data1.csv")
```

Let's take a look at the data.
```{r}
str(d)
```

I'm going to find how many recalled their words and how many did not recall the target 
words.


```{r}
summary(d$Remember)
```

Let's also do this for congruence to see how 
many participated in congruent and incongruent conditions

```{r}
summary(d$Congruence)
```


We need to tranform the variables we will be using into factor variables. 

```{r}
d$Remember<-as.factor(d$Remember)
d$Congruence<-as.factor(d$Congruence)
```

##Figure

To visualize the data as presented, I will create a histogram of the valence rankings 
as the pertain to how frequent they appear.
```{r}
hist(d$Valence)
```

```{r, eval=FALSE}
library(ggplot2)
```
```{r,include=FALSE}
library(ggplot2)
```



##Primary Analysis

We will us a Chi Square test to compare counts of categorical responses between the recalled words and whether or not the participants were in a congruent condition.  

```{r}
tab<-table(d$Remember,d$Congruence)
tab
```

     N  Y
  N  5  1
  Y 11 17
  
These are the frequencies in which the participants remembered the word and whether or not it was congruent.  

```{r}
chisq.test(d$Remember,d$Remember)
```

Chi- Squared= 27, p-value=1.598-07

The p-value is less than the .05 significance level.  Because of this p- value we would reject 
the null hypothesis. The colored words were recalled at greater rates. 
The emotionality of the words and their congruence with the color (red/negative or green/positive)
were not independent of each other.  
This insinuates that color does, in fact, enhance memory, but whether or not the color induces
emotion- enhanced memory was not shown.  



