---
title: "Data1 analysis"
output: html_document
---
#Data analysis and figure creation for Color Memory and Emotion Experiment on Youtube

###Kayli Peters

##Introduction
This file was used to analyze data from my Color Memory and Emotion Experiment, 
https://www.youtube.com/watch?v=U6WmtoIuaXY.  
All materials, including consent, tasks, and debriefing can be accessed 
in the previous link provided.  **Note**: The link may not be accessible on mobile devices.  It is suggested to 
work on a laptop or desktop computer.  

These data represent 35 participants who reported participating 
in existing conditions and emailed me their data.  
Those participants that did not include the condition
were not included in this data set.  

Although several variables were included.  Only two were of interest to
be analyzed here.  The variables representing Congruence and Recall(Remember) were the 2 analyzed.  These data were analyzed and presented on the poster.  

###Preparing data for analysis 

```{r}
d<-read.csv("data1.csv")
```

We need to tranform the variables we will be using into factor variables. 

```{r}
d$Remember<-as.factor(d$Remember)
d$Congruence<-as.factor(d$Congruence)
```

##Primary Analysis








